[dcpo_demsupport]

### 2020-08-07 paper/dcpo_demsupport.Rmd
revised the `estimated_dcpo`

estimate_dcpo_pooled <- function(aModel) {
  result_dcpo_1k <- map(df_dcpo, function(aDataset) {
    plm::plm(aModel,
             model = "pooling",
             data = aDataset)
  })

  result_betas_dcpo_1k <-
    mitools::MIextract(result_dcpo_1k, fun = coef)
  result_vars_dcpo_1k <-
    mitools::MIextract(result_dcpo_1k, fun = vcovBK_se)

@@

df_result_dcpo <- map(mod_ls, estimate_dcpo_pooled)

estimate_dcpo_gmm <- function(aModel) {
  result_dcpo_1k <- map(df_dcpo, function(aDataset) {
    pgmm(as.formula(aModel), effect="individual", model="onestep", transformation="ld", indexes=c("Country", "Year"), data = aDataset)
  })

  result_betas_dcpo_1k <-
    mitools::MIextract(result_dcpo_1k, fun = coef)
  result_vars_dcpo_1k <-
    mitools::MIextract(result_dcpo_1k, fun = vcovHC_se)

@@

df_result_dcpo[3:4] <- map(mod_ls, estimate_dcpo_gmm)

>>>>

estimate_dcpo <- function(aModel, aType = "pooling") {
  if (aType == "gmm") {
    result_dcpo_1k <- map(df_dcpo, function(aDataset) {
      pgmm(
        as.formula(aModel),
        effect = "individual",
        model = "onestep",
        transformation = "ld",
        indexes = c("Country", "Year"),
        data = aDataset
      )
    })

    result_vars_dcpo_1k <-
      mitools::MIextract(result_dcpo_1k, fun = vcovHC_se)

  } else {
    result_dcpo_1k <- map(df_dcpo, function(aDataset) {
      plm::plm(aModel,
               model = "pooling",
               data = aDataset)
    })

    result_vars_dcpo_1k <-
      mitools::MIextract(result_dcpo_1k, fun = vcovBK_se)
  }

@@

df_result_dcpo <- map(mod_ls, estimate_dcpo)

@@

df_result_dcpo[3] <- map(mod_ls[[1]], estimate_dcpo, aType = "gmm")
